Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-14 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:14	21:20:17	(Wed14.Oct)

In many cases MVDR can improve the contrast and resolution of active sonar images compared to conventional static methods~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}. However, while the computational complexity of conventional beamformers are linear with the number of channels, O($M$), MVDR is at O($M^3$). This makes MVDR impracticable and sometimes infeasible. We have shown in previous studies that MVDR's complexity can be reduced, and its implementation accelerated significantly using graphics computing units (GPUs)~\cite{Buskenes2014,Asen2013}. However, even this near optimal implementation is slow compared to DAS.

>>>>

In many cases MVDR can improve the contrast and resolution of active sonar images compared to conventional static methods~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}. However, while the computational complexity of conventional beamformers are linear with the number of channels, O($M$), MVDR is at O($M^3$). This is because MVDR relies on estimating and inverting a covariance matrix. When the number of channels are less than 32, we have shown that the estimation step is the bottleneck and how this can be how complexity can be reduced and its implementation accelerated significantly using graphics computing units (GPUs)~\cite{Buskenes2014}. In clinical ultrasound where the systems tend to be larger and the beams are focused we have ported the same algorithm to beamspace for  performance~\cite{Asen2013}. Asl  a space reduction technique , which is a technique to . However, even this near optimal implementation is slow compared to DAS.
